---
title: "flat_first.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(parallel)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
datafile=system.file("M64.RData", package = "grouptheory")
m64=load(datafile)
m64
```


# Occurrences

```{r function-Occurrences}
#' Occurrences
#'
#' @param v,M A matrix "M" and a row vector "v".
#'
#' @return
#' The number of times "v" is a row vector of "M".
#' @export
#'
#' @examples
Occurrences=function(v,M){
  l=length(v)
  for(s in 1:l){
    a=M[,s]
    ind=which(a==v[s])
    M=rbind(M[ind,])
  }
  return(length(ind))
}
```

```{r examples-Occurrences}
Occurrences(c(2,3),rbind(c(1,2),c(2,3),c(2,3),c(7,8)))

# Example with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply my function
Occurrences(c(1,2,4,8,16,32,7,1,1),M64)
```

```{r tests-Occurrences}
test_that("Occurrences works properly and show error if needed", {
  expect_true(Occurrences(c(2,3),rbind(c(1,2),c(2,3),c(2,3),c(7,8)))==2)
  expect_true(Occurrences(c(2,3),rbind(c()))==0)
  expect_error(Occurrences("text"))
})

# Test with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply test on my function
test_that("Occurrences works properly with internal dataset", {
  expect_equal(Occurrences(c(1,2,4,8,16,32,7,1,1),M64),1)
})
```

# Smallest

```{r function-Smallest}
#' Smallest
#'
#' @param M A matrix "M".
#'
#' @return
#' The smallest row of "M" in lexicographical order.
#' @export
#'
#' @examples
Smallest=function(M){
  n=ncol(M)
  for(j in 1:n){
    if(nrow(M)>1){
      x=M[,j]
      ind=which(x==min(x))
      M=rbind(M[ind,])
    }
  }
  return(M[1,])
}
```

```{r examples-Smallest}
Smallest(rbind(c(1,2),c(2,3),c(2,3),c(7,8)))

# Example with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply my function
Smallest(M64)
```

```{r tests-Smallest}
test_that("Smallest works properly and show error if needed", {
  expect_equal(Smallest(rbind(c(1,2),c(2,3),c(2,3),c(7,8))),c(1,2))
})

# Test with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply test on my function
test_that("Smallest works properly with internal dataset", {
  expect_equal(Smallest(M64),c(1,2,4,8,16,32,7,1,1))
})
```

# FindRows

```{r function-FindRows}
#' FindRows
#'
#' @param v,M A row vector "v" and a Matrix "M".
#'
#' @return
#' The indices of all the rows of "M" approximately equal to "v". The comparison is made only where "M" is non-negative.
#' @export
#'
#' @examples
FindRows=function(v,M){
  l=length(v); ll=ncol(M); out=c()
  if(l==ll){
    for(j in 1:nrow(M)){
      Mj=M[j,]; Dj=abs(Mj-v); Dj=Dj[Mj>=0]
      if(sum(Dj)<0.5){out=c(out,j)}
    }
  }
  return(out)
}
```

```{r examples-FindRows}
FindRows(c(2,3,5),rbind(c(1,2,7),c(2,3,5),c(2,3,-10),c(7,8,5)))

# Example with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply my function
FindRows(c(1,2,4,8,16,32,7,1,1),M64)
```

```{r tests-FindRows}
test_that("FindRows works properly and show error if needed", {
  expect_equal(FindRows(c(2,3,5),rbind(c(1,2,7),c(2,3,5),c(2,3,-10),c(7,8,5))),c(2,3))
  expect_error(FindRows("text"))
})

# Test with your dataset in "inst/"
datafile=system.file("M64.RData",package="grouptheory")
load(datafile)
# Apply test on my function
test_that("FindRows works properly with internal dataset", {
  expect_equal(FindRows(c(1,2,4,8,16,32,7,1,1),M64),1)
})
```

# Divisors

```{r function-Divisors}
#' Divisors
#'
#' @param n A natural number "n".
#'
#' @return
#' The divisors of "n" except 1.
#' @export
#'
#' @examples
Divisors=function(n){
  out=c()
  for(j in 2:n){if(n%%j==0){out=c(out,j)}}
  return(out)
}
```

```{r examples-Divisors}
Divisors(12)
```

```{r tests-Divisors}
test_that("Divisors works properly and show error if needed", {
  expect_equal(Divisors(12),c(2,3,4,6,12))
})
```

# AfromM

```{r function-AfromM}
#' AfromM
#'
#' @param M A list of square matrices "M" with the Identity as its first matrix
#'
#' @return
#' The Cayley table "A" of the Matrix group "M"
#' @export
#'
#' @examples
AfromM=function(M){
  lM=length(M)
  wo=function(i){
    Mi=M[[i]]; out=c()
    for(j in 1:lM){
      A=Mi%*%M[[j]]
      for(s in 1:lM){
        if(sum((A-M[[s]])^2)<0.05){a=s;break}
      }
      out=c(out,a); rm(a)
    }
    return(out)
  }
  A=matrix(unlist(parallel::mclapply(c(1:lM),wo,mc.cores=parallel::detectCores())),byrow=T,nrow=lM,ncol=lM)
  return(A)
}
```

# AfromM2

```{r function-AfromM2}
#' AfromM2
#'
#' @param M,silent A list of square matrices "M" with the Identity as its first matrix and an option
#'
#' @return
#' The Cayley table "A" of the Matrix group "M"
#' @export
#'
#' @examples
AfromM2=function(M,silent=T){
  lM=length(M); A=c()
  woo=function(i,j){
    A=M[[i]]%*%M[[j]]
    for(s in 1:lM){
      if(sum((A-M[[s]])^2)<0.05){a=s;break}
    }
    return(a)
  }
  wo=function(i){
    woi=function(j){return(woo(i,j))}
    return(unlist(parallel::mclapply(c(1:lM),woi,mc.cores=parallel::detectCores())))
  }
  for(i in 1:lM){
    A=rbind(A,wo(i))
    if(silent==F){print(i/lM)}
  }
  return(A)
}
#list(rbind(c(1,0,0),c(0,1,0),c(0,0,1)),rbind(c(1,0,0),c(0,0,1),c(0,1,0)),rbind(c(0,1,0),c(1,0,0),c(0,0,1)),rbind(c(0,1,0),c(0,0,1),c(1,0,0)),rbind(c(0,0,1),c(1,0,0),c(0,1,0)),rbind(c(0,0,1),c(0,1,0),c(1,0,0)))
```

# Span

```{r function-Span}
#' Span
#'
#' @param A,w The Cayley table "A" of a group and a vector "w" of elements in the group
#'
#' @return
#' The vector of elements in the subgroup of "A" generated by "w".
#' @export
#'
#' @examples
Span=function(A,w){
  n=nrow(A); a=unique(c(1,w))
  for(s in 1:n){
    an=unique(sort(A[a,a]))
    if(length(an)==length(a)){
      a=an
      break
    }
    a=an
  }
  return(a)
}
```

# Relabel

```{r function-Relabel}
#' Relabel
#'
#' @param A,w The Cayley table "A" of a group and a vector "w" of elements in a subgroup
#'
#' @return
#' The Cayley table "A" of the subgroup.
#' @export
#'
#' @examples
Relabel=function(A,w){
  l=length(w)
  Aw=A[w,w]; m=Aw[1,]
  fu=function(i){return(which(m==i))}
  return(apply(Aw,c(1,2),fu))
}
```

# OrderStructure

```{r function-OrderStructure}
#' OrderStructure
#'
#' @param A The Cayley table "A" of a group.
#'
#' @return
#' The number of elements of each possible orders except one. That is of each non-one divisor of the size of the group.
#' @export
#'
#' @examples
OrderStructure=function(A){
  l=nrow(A)
  ord=c()
  for(j in 2:l){
    a=j
    for(s in 1:l){
      if(a==1){break}
      a=A[j,a]
    }
    ord=c(ord,s)
  }
  out=c()
  for(s in 2:l){
    if(l%%s==0){
      out=c(out,length(which(ord==s)))
    }
  }
  return(out)
}
```

# Inverse

```{r function-Inverse}
#' Inverse
#'
#' @param A The Cayley table "A" of a group
#'
#' @return
#' The vector with the inverse of all the elements in the group.
#' @export
#'
#' @examples
Inverse=function(A){
  n=nrow(A); I=c(1)
  for(j in 2:n){
    I=c(I,which(A[j,]==1))
  }
  return(I)
}
```

# Conjugates

```{r function-Conjugates}
#' Conjugates
#'
#' @param A,I,w The Cayley table "A" of a group, the list of inverses "I", and a sequence of elements "w".
#'
#' @return
#' A matrix whose rows are the different collections of elements in "A" conjugate to "w".
#' @export
#'
#' @examples
Conjugates=function(A,I,w){
  n=nrow(A)
  out=rbind(w)
  for(g in 2:n){
    out=rbind(out,sort(A[g,A[w,I[g]]]))
  }
  out=unique(out)
  return(out)
}
```

# XfromA

```{r function-XfromA}
#' XfromA
#'
#' @param A,silent The Cayley table "A" of a group and a parameter
#'
#' @return
#' A list of all the subgroups of "A" up to conjugacy. Each element of the list is a vector containing 1. its size, 2. its occurrences, 3. its rank ie the minimal size of a generating set, 4. the vector of the elements of one of its representatives.
#' @export
#'
#' @examples
XfromA=function(A,silent=T){
  NewPart=function(A,B){
    C=c()
    if(length(B)>0 & length(A)>0){
      for(i in 1:length(A)){
        a=A[[i]]; s=1
        for(j in 1:length(B)){
          b=B[[j]]
          if(length(a[-3])==length(b[-3])){if(sum((a[-3]-b[-3])^2)==0){s=0; break}}
        }
        if(s==1){C[[length(C)+1]]=a}
      }
    }
    else{C=A}
    return(C)
  }
  up=function(A,IA,O1,neworder){
    n=nrow(A); L=Divisors(n); ind=c(1:n); ii=length(O1)
    upsmall=function(i){
      O2=list(); oi=O1[[i]][-c(1:3)]
      for(l in L){assign(as.matrix(paste0("W",l)),rbind(c()))}
      if(length(oi<n)){
        for(j in ind[-oi]){
          w=Span(A,sort(c(oi,j))); l=length(w)
          assign(paste0("W",l),rbind(get(paste0("W",l)),w))
        }
      }
      for(l in L){
        if(length(get(paste0("W",l)))>0){
          W=unique(get(paste0("W",l))); V=c()
          for(j in 1:nrow(W)){
            w=W[j,]
            if(Occurrences(w,V)==0){
              Z=Conjugates(A,IA,w); V=rbind(V,Z)
              O2[[length(O2)+1]]=c(l,nrow(Z),neworder,Smallest(Z))
            }
          }
        }
      }
      for(l in L){rm(list=paste0("W",l))}
      return(O2)
    }
    return(unique(unlist(parallel::mclapply(c(1:ii),upsmall,mc.preschedule=F,mc.cores=parallel::detectCores()),recursive=F)))
  }
  
  IA=Inverse(A); out=1; X0=list(c(1,1,0,1)); if(silent==F){print(c(0,length(X0)))}
  X1=up(A,IA,X0,1); if(silent==F){print(c(1,length(X1)))}
  XX=append(X0,X1)
  for(s in 2:10){
    assign(paste0("X",s),up(A,IA,get(paste0("X",s-1)),s))
    for(j in 1:(s-1)){
      assign(paste0("X",s),NewPart(get(paste0("X",s)),get(paste0("X",s-j))))
      if(length(get(paste0("X",s)))==0){break}
    }
    l=length(get(paste0("X",s)))
    if(l==0){break}
    if(silent==F){print(c(s,l))}
    XX=append(XX,get(paste0("X",s)))
  }
  return(XX)
}
```

# NumberOfSubgroups

```{r function-NumberOfSubgroups}
#' NumberOfSubgroups
#'
#' @param A The Cayley table "A" of a group
#'
#' @return
#' A couple with the number of subgroups up to conjugacy and overall.
#' @export
#'
#' @examples
NumberOfSubgroups=function(A){
  X=XfromA(A); l=length(X); s=0
  for(j in 1:l){s=s+X[[j]][2]}
  return(c(l,s))
}
```

# IsAbelian

```{r function-IsAbelian}
#' IsAbelian
#'
#' @param A The Cayley table "A" of a group
#'
#' @return
#' 1 if the group is Abelian 0 otherwise.
#' @export
#'
#' @examples
IsAbelian=function(A){
  out=0
  if(sum((A-t(A))^2)<0.5){out=1}
  return(out)
}
```

# EfromAX

```{r function-EfromAX}
#' EfromAX
#'
#' @param A,X,silent The Cayley table "A" of a group and its list of up-to-conjugacy-subgroups "X" and a parameter.
#' 
#' @return
#' The adjacency matrix of its up-to-conjugacy-subgroups, where i is linked to j if there is a subgroup of conjugacy-type i that is an immediate subgroup of some subgroup of conjugacy-type j. By immediate subgroup we mean that there is no intermediate subgroup in between.
#' @export
#'
#' @examples
EfromAX=function(A,X,silent=T){
  I=Inverse(A); nn=length(X); ind=1:nn; S=c(); SS=matrix(nrow=nn,ncol=nn)
  fuu=function(j){return(Conjugates(A,I,X[[j]][-c(1:3)]))}
  TT=parallel::mclapply(ind,fuu,mc.cores=parallel::detectCores())
  if(silent==F){print("ok")}
  for(i in ind){
    Ti=rbind(TT[[i]]); l1=ncol(Ti); lc=nrow(Ti)
    fu=function(j){
      out=0
      w2=X[[j]][-c(1:3)]; l2=length(w2)
      if(l1<l2){
        for(s in 1:lc){
          if(length(intersect(Ti[s,],w2))==l1){out=1;break}
        }
      }
      return(out)
    }
    S=rbind(S,unlist(parallel::mclapply(ind,fu,mc.cores=parallel::detectCores())))
    if(silent==F){print(i/nn)}
  }
  for(i in ind){
    for(j in ind){
      o=F
      if(S[i,j]==1){
        o=T
        for(k in ind[-c(i,j)]){
          if(S[i,k]==1 & S[k,j]==1){o=F;break}
        }
      }
      SS[i,j]=o
    }
  }
  return(SS)
}
```

# PrimeFactors

```{r function-PrimeFactors}
#' PrimeFactors
#'
#' @param x A natural number x
#'
#' @return
#' All its divisors of the form p^k
#' @export
#'
#' @examples
PrimeFactors=function(x){
  if(x==1){factors=c(1)}
  else{
  i=2; factors=c()
  while(x>=i){
    if(! x %% i){
      factors=c(factors,i)
      x=x/i
      i=i-1
    }
    i=i+1
  }
  }
  return(factors)
}
```

# relx

```{r function-relx}
#' relx
#'
#' @param p,q two natural numbers
#'
#' @return
#' t
#' @export
#'
#' @examples
relx=function(p,q){
  out=0
  if(q-p*floor(q/p)==1){out=1}
  return(out)
}
```

# rel

```{r function-rel}
#' rel
#'
#' @param p,q two natural numbers
#'
#' @return
#' t
#' @export
#'
#' @examples
rel=function(p,q){
  out=0
  if(relx(p,q)==1 | relx(q,p)==1){out=1}
  return(out)
}
```

# Efromv

```{r function-Efromv}
#' Efromv
#'
#' @param v a list of primes
#'
#' @return
#' t
#' @export
#'
#' @examples
Efromv=function(v){
  l=length(v); E=matrix(rep(0,l^2),nrow=l,ncol=l)
  for(i in 1:l){
    for(j in 1:l){
      if(relx(v[i],v[j])){E[j,i]=1}
    }
  }
  return(E)
}
```

# Efromx

```{r function-Efromx}
#' Efromx
#'
#' @param x a natural number
#'
#' @return
#' t
#' @export
#'
#' @examples
Efromx=function(x){return(Efromv(PrimeFactors(x)))}
```

# remov

```{r function-remov}
#' remov
#'
#' @param x a natural number
#'
#' @return
#' t
#' @export
#'
#' @examples
remov=function(x){
  v=PrimeFactors(x); E=Efromv(v); ind=c()
  for(j in 1:length(v)){
    if(length(v[v==v[j]])==1 & sum(E[j,])==0 & sum(E[,j])==0){ind=c(ind,j)}
  }
  if(length(ind)>0){out=v[-ind]}
  else{out=v}
  return(out)
}
```

# Is1Number

```{r function-Is1Number}
#' Is1Number
#'
#' @param x A natural number x
#'
#' @return
#' 1 if there is only one group of order x, 0 otherwise
#' @export
#'
#' @examples
Is1Number=function(x){
  v=PrimeFactors(x); u=unique(v); out=1
  if(length(v)!=length(u)){out=0}
  else{
    if(length(remov(x))>0){out=0}
  }
  return(out)
}
```

# Is2Number

```{r function-Is2Number}
#' Is2Number
#'
#' @param x A natural number
#'
#' @return
#' 1 or 2 if there are exactly two groups of order x, 0 otherwise.
#' @export
#'
#' @examples
Is2Number=function(x){
  v=PrimeFactors(x); u=unique(v); out=0
  if(length(v)==length(u)){
    if(length(remov(x))==2){out=1}
  }
  if(length(u)==length(v)-1){
    E=Efromv(u)
    if(sum(E)==0){
      fr=unlist(lapply(v,function(x){return(length(which(v==x)))}))
      p=v[fr==2][1]; s=0
      for(j in 1:length(u)){
        if(p!=u[j] & rel(p^2,u[j])==1){s=s+1}
      }
      if(s==0){out=2}
    }
  }
  return(out)
}
```

# Is3Number

```{r function-Is3Number}
#' Is1Number
#'
#' @param x A natural number
#'
#' @return
#' 1 if there is only one group of order x, 0 otherwise
#' @export
#'
#' @examples
Is3Number=function(x){
  v=PrimeFactors(x); u=unique(v); out=0
  if(length(v)==length(u)){
    uu=remov(x)
    if(length(uu)==3){
      if(sum(abs(Efromv(uu)-rbind(c(0,0,0),c(1,0,0),c(0,1,0))))==0){out=1}
    }
  }
  if(length(u)==length(v)-1){
    E=Efromv(u)
    if(sum(E)==0){
      fr=unlist(lapply(v,function(x){return(length(which(v==x)))}))
      p=v[fr==2][1]; s=0
      for(j in 1:length(u)){
        if(p!=u[j] & rel(p^2,u[j])==1){s=s+1}
      }
      if(s==1){out=2}
    }
  }
  return(out)
}
```

# GroupId

```{r function-GropuId}
#' GroupId
#'
#' @param A,w,rk The Cayley table "A" of a group, a vector "w" of elements of a subgroup and the rank of this subgroup.
#'
#' @return the group id
#' 
#' @export
#'
#' @examples
GroupId=function(A,w,rk){
  g1=c(1,2,3,5,7,11,13,15,17,19,23,29,31,33,35,37,41,43,47,51,53,59,61,65,67,69,71,73,77,79,83,85,87,89,91,95,97,101,103,107,109,113,115,119,123,127,131,133,137,139,141,143,145,149,151,157,159,161,163,167,173,177,179,181,185,187,191,193,197,199,209,211,213,215,217,221,223,227,229,233,235,239,241,247,249,251,255,257,259,263,265,267,269,271,277,281,283,287,293,295,299,303,307,311,313,317,319,321,323,329,331,335,337,339,341,345,347,349,353,359,365,367,371,373,377,379,383,389,391,393,395,397,401,403,407,409,411,413,415,419,421,427,431,433,435,437,439,443,445,447,449,451,455,457,461,463,467,469,473,479,481,485,487,491,493,499,501,503,509,511,515,517,519,521,523,527,533,535,537,541,545,547,551,553,557,559,561,563,565,569,571,573,577,581,583,587,589,591,593,595,599,601,607,611,613,617,619,623,629,631,635,641,643,647,649,653,659,661,665,667,671,673,677,679,681,683,685,691,695,697,699,701,703,705,707,709,713,717,719,721,727,731,733,739,743,745,749,751,753,757,761,763,767,769,771,773,779,781,785,787,789,793,795,797,799,803,805,807,809,811,815,817,821,823,827,829,835,839,843,851,853,857,859,863,865,869,871,877,879,881,883,885,887,893,895,899,901,907,911,913,917,919,923,929,933,937,941,943,947,949,951,953,957,959,965,967,971,973,977,983,985,989,991,995,997,1001,1003,1007,1009,1013,1019,1021,1031,1033,1037,1039,1041,1043,1049,1051,1057,1059,1061,1063,1067,1069,1073,1077,1079,1087,1091,1093,1097,1099,1103,1105,1109,1111,1115,1117,1121,1123,1129,1133,1135,1139,1141,1145,1147,1149,1151,1153,1157,1159,1163,1165,1167,1169,1171,1173,1177,1181,1187,1189,1193,1195,1199,1201,1203,1207,1211,1213,1217,1219,1223,1229,1231,1235,1237,1241,1243,1245,1247,1249,1253,1257,1259,1261,1267,1271,1273,1277,1279,1283,1285,1289,1291,1293,1295,1297,1301,1303,1307,1309,1313,1315,1319,1321,1327,1329,1333,1335,1337,1339,1343,1345,1347,1349,1351,1353,1357,1361,1363,1367,1373,1381,1383,1385,1387,1391,1393,1397,1399,1401,1403,1409,1411,1415,1417,1423,1427,1429,1433,1437,1439,1441,1447,1451,1453,1457,1459,1463,1465,1469,1471,1473,1479,1481,1483,1487,1489,1493,1495,1499,1501,1507,1509,1511,1513,1517,1523,1527,1529,1531,1535,1537,1541,1543,1547,1549,1551,1553,1559,1561,1563,1565,1567,1571,1577,1579,1583,1585,1589,1591,1597,1601,1603,1605,1607,1609,1613,1615,1619,1621,1627,1631,1633,1637,1639,1643,1645,1649,1651,1657,1661,1663,1667,1669,1671,1679,1685,1687,1689,1691,1693,1695,1697,1699,1707,1709,1717,1721,1723,1727,1729,1733,1735,1739,1741,1745,1747,1749,1753,1757,1759,1761,1763,1765,1769,1777,1779,1781,1783,1787,1789,1793,1795,1797,1799,1801,1807,1811,1817,1819,1823,1829,1831,1835,1837,1841,1843,1847,1851,1853,1855,1861,1865,1867,1871,1873,1877,1879,1883,1885,1889,1891,1895,1897,1901,1903,1907,1909,1913,1915,1919,1921,1923,1927,1931,1933,1937,1939,1941,1943,1945,1947,1949,1951,1955,1957,1959,1961,1963,1969,1973,1977,1979,1981,1985,1987,1991,1993,1997,1999,2001,2003,2011,2017,2021,2027,2029,2031,2033,2039,2045,2047)
  g2ab=c(4,9,25,45,49,99,121,153,169,175,207,245,261,289,325,361,369,423,425,475,477,529,531,539,575,637,639,725,747,765,801,833,841,845,847,909,925,931,961,963,1017,1035,1075,1127,1175,1179,1233,1305,1325,1341,1369,1445,1475,1503,1519,1557,1573,1611,1675,1681,1683,1719,1773,1813,1825,1849,1859,1975,2009,2023,2043)
  g2no=c(6,10,14,21,22,26,34,38,39,46,55,57,58,62,74,82,86,93,94,105,106,111,118,122,129,134,142,146,155,158,165,166,178,183,194,195,201,202,203,205,206,214,218,219,226,231,237,253,254,262,274,278,285,291,298,301,302,305,309,314,326,327,334,346,355,357,358,362,381,382,385,386,394,398,417,422,429,446,453,454,458,466,471,478,482,483,489,497,502,505,514,526,538,542,543,554,555,562,566,579,586,597,614,615,622,626,627,633,634,645,655,662,663,669,674,687,689,694,698,706,715,718,723,734,737,746,755,758,759,766,778,791,794,802,813,818,831,838,842,849,861,862,866,878,886,889,897,898,905,914,921,922,926,934,935,939,955,958,969,974,979,982,987,993,998,1005,1006,1011,1015,1018,1023,1027,1042,1045,1046,1047,1055,1065,1081,1082,1085,1094,1095,1101,1113,1114,1119,1126,1131,1137,1138,1142,1154,1174,1185,1186,1191,1198,1202,1205,1214,1221,1226,1227,1234,1238,1239,1255,1262,1263,1282,1286,1294,1299,1306,1311,1317,1318,1322,1346,1354,1355,1366,1371,1379,1382,1389,1402,1405,1418,1419,1435,1438,1454,1455,1461,1466,1477,1478,1486,1497,1502,1505,1514,1515,1522,1538,1545,1546,1555,1569,1574,1581,1594,1595,1599,1618,1622,1623,1635,1641,1642,1646,1653,1654,1655,1658,1673,1678,1703,1706,1711,1713,1714,1718,1726,1731,1743,1751,1754,1762,1766,1771,1774,1785,1803,1814,1821,1822,1833,1838,1839,1857,1858,1869,1874,1882,1887,1893,1894,1905,1906,1929,1934,1942,1954,1965,1966,1967,1982,1983,1994,2005,2013,2015,2018,2019,2026,2035,2038,2041,2042)
  g3ab=c(75,363,867,1183,1275,1587,1725,1805)
  g3no=c(609,1265,1491)
  go=setdiff(c(1:127,168,200),c(g1,g2ab,g2no,g3ab,g3no,64,96))
  
  out=0
  l=length(w)
  if(l%in%g1 | Is1Number(l)==1 | rk==1){out=-1} #cyclic
  if((l%in%g2ab | Is2Number(l)==2) & rk>1){out=-2} #the only non cyclic abelian group
  if((l%in%g2no | Is2Number(l)==1) & rk>1 & l%%2==0){out=-3} #dihedral
  if((l%in%g2no | Is2Number(l)==1) & rk>1 & l%%2!=0){out=-4} #the only non abelian group
  if((l%in%g3ab | Is3Number(l)==2) & rk>1){
    Aw=Relabel(A,w)
    ab=IsAbelian(Aw)
    if(ab==1){out=-5} #the only non cyclic abelian group
    if(ab==0){out=-6} #the only non abelian group
  }
  if((l%in%g3no | Is3Number(l)==1) & rk>1){out=-7
    #Aw=Relabel(A,w)
    #ab=IsAbelian(Aw)
    #if(ab==1){out=-5} #the only non cyclic abelian group
    #if(ab==0){out=-6} #the only non abelian group
  }
  if(l%in%c(go,64,96,128,144,160,192,240,288,320,360,384,400,480,576,600,640,720,960,1200,1440)){#256,1152,
      #216,224,324,336,352,416,432,448,486,504,512,528,540,544,560,576,608,624,648,672,704,729,736,756,768,784,792,800,810,816,832,840,864,880,896,900,912,928,936,972,992,1000,
    #############################
if(l%in%go){
#4: 28,30,44,63,66,70,76,92,102,117,124,130,138,154,170,172,174,182,188,190,230,236,238,246,266,268,275,279,282,284,286,290,315,316,318,322,332,354,370,374,387,412,418,426,428,430,434,442,465,470,494,495,498,508
M28=cbind(# 2^2 7
  c(1,1,15,3),#2
  c(14,2,0,0),#4
  c(6,6,6,6),#7
  c(6,6,6,18),#14
  c(0,12,0,0),#28
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M30=cbind(# 2 3 5
  c(3,5,15,1),#2
  c(2,2,2,2),#3
  c(4,4,4,4),#5
  c(0,10,0,2),#6
  c(12,0,0,4),#10
  c(8,8,8,8),#15
  c(0,0,0,8),#30
  c(2,2,2,1),#rk
  c(0,0,0,1)#Ab
)
M44=cbind(# 2^2 11
  c(1,1,23,3),#2
  c(22,2,0,0),#4
  c(10,10,10,10),#11
  c(10,10,10,30),#22
  c(0,20,0,0),#44
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M63=cbind(# 3^2 7
  c(2,2,44,8),#3
  c(6,6,6,6),#7
  c(42,6,0,0),#9
  c(12,12,12,48),#21
  c(0,36,0,0),#63
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M66=cbind(# 2 3 11
  c(3,11,33,1),#2
  c(2,2,2,2),#3
  c(0,22,0,2),#6
  c(10,10,10,10),#11
  c(30,0,0,10),#22
  c(20,20,20,20),#33
  c(0,0,0,20),#66
  c(2,2,2,1),#rk
  c(0,0,0,1)#Ab
)
M70=cbind(# 2 5 7
  c(5,7,35,1),#2
  c(4,4,4,4),#5
  c(6,6,6,6),#7
  c(0,28,0,4),#10
  c(30,0,0,6),#14
  c(24,24,24,24),#35
  c(0,0,0,24),#70
  c(2,2,2,1),#rk
  c(0,0,0,1)#Ab
)
M76=cbind(# 2^2 19
  c(1,1,39,3),#2
  c(38,2,0,0),#4
  c(18,18,18,18),#19
  c(18,18,18,54),#38
  c(0,36,0,0),#76
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M92=cbind(# 2^2 23
  c(1,1,47,3),#2
  c(46,2,0,0),#4
  c(22,22,22,22),#23
  c(22,22,22,66),#46
  c(0,44,0,0),#92
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M102=cbind(# 2 3 17
  c(3,17,51,1),#2
  c(2,2,2,2),#3
  c(0,34,0,2),#6
  c(16,16,16,16),#17
  c(48,0,0,16),#34
  c(32,32,32,32),#51
  c(0,0,0,32),#102
  c(2,2,2,1),#rk
  c(0,0,0,1)#Ab
)
M117=cbind(# 3^2 13
  c(2,2,80,8),#3
  c(78,6,0,0),#9
  c(12,12,12,12),#13
  c(24,24,24,96),#39
  c(0,72,0,0),#117
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
M124=cbind(# 2^2 31
  c(1,1,63,3),#2
  c(62,2,0,0),#4
  c(30,30,30,30),#31
  c(30,30,30,90),#62
  c(0,60,0,0),#124
  c(2,1,2,2),#rk
  c(0,1,0,1)#Ab
)
#5: 8,12,18,20,27,50,52,68,98,116,125,135,148,164,171,212,242,244,273,292,297,333,338,343,356,388,399,404,436,452,459
M8=cbind(# 2^3
  c(1,3,5,1,7),#2
  c(2,4,2,6,0),#4
  c(4,0,0,0,0),#8
  c(1,2,2,2,3),#rk
  c(1,1,0,0,1)#Ab
)
M12=cbind(# 2^2 3
  c(1,1,3,7,3),#2
  c(2,2,8,2,2),#3
  c(6,2,0,0,0),#4
  c(2,2,0,2,6),#6
  c(0,4,0,0,0),#12
  c(2,1,2,2,2),#rk
  c(0,1,0,0,1)#Ab
)
M18=cbind(# 2 3^2
  c(9,1,3,9,1),#2
  c(2,2,8,8,8),#3
  c(0,2,6,0,8),#6
  c(6,6,0,0,0),#9
  c(0,6,0,0,0),#18
  c(2,1,2,3,2),#rk
  c(0,1,0,0,1)#Ab
)
M20=cbind(# 2^2 5
  c(1,1,5,11,3),#2
  c(10,2,10,0,0),#4
  c(4,4,4,4,4),#5
  c(4,4,0,4,12),#10
  c(0,8,0,0,0),#20
  c(2,1,2,2,2),#rk
  c(0,1,0,0,1)#Ab
)
M27=cbind(# 3^3
  c(2,8,26,8,26),#3
  c(6,18,0,18,0),#9
  c(18,0,0,0,0),#27
  c(1,2,2,2,3),#rk
  c(1,1,0,0,1)#Ab
)
M50=cbind(# 2 5^2
  c(25,1,5,25,1),#2
  c(4,4,24,24,24),#5
  c(0,4,20,0,24),#10
  c(20,20,0,0,0),#25
  c(0,20,0,0,0),#50
  c(2,1,2,3,2),#rk
  c(0,1,0,0,1)#Ab
)
M52=cbind(# 2^2 13
  c(1,1,13,27,3),#2
  c(26,2,26,0,0),#4
  c(12,12,12,12,12),#13
  c(12,12,0,12,36),#26
  c(0,24,0,0,0),#52
  c(2,1,2,2,2),#rk
  c(0,1,0,0,1)#Ab
)
M68=cbind(# 2^2 17
  c(1,1,17,35,3),#2
  c(34,2,34,0,0),#4
  c(16,16,16,16,16),#17
  c(16,16,0,16,48),#34
  c(0,32,0,0,0),#68
  c(2,1,2,2,2),#rk
  c(0,1,0,0,1)#Ab
)
M98=cbind(#2*7^2
  c(49,1,7,49,1),#2
  c(6,6,48,48,48),#7
  c(0,6,42,0,48),#14
  c(42,42,0,0,0),#49
  c(0,42,0,0,0),#98
  c(2,1,2,3,2),#rk
  c(0,1,0,0,1)#Ab
)
M116=cbind(#2^2*29
  c(1,1,29,59,3),#2
  c(58,2,58,0,0),#4
  c(28,28,28,28,28),#29
  c(28,28,0,28,84),#58
  c(0,56,0,0,0),#116
  c(2,1,2,2,2),#rk
  c(0,1,0,0,1)#Ab
)
M125=cbind(#5^3
  c(4,24,124,24,124),#5
  c(20,100,0,100,0),#25
  c(100,0,0,0,0),#125
  c(1,2,2,2,3),#rk
  c(1,1,0,0,1)#Ab
)
#6: 42,78,110,114,147,186,222,225,258,310,366,402,406,410,438,474,506,507,525,582,602,610,618,654,710,735,762,834,906,942,975,978,994,1010
M42=cbind(
  c(7,1,3,7,21,1),#2
  c(14,14,2,2,2,2),#3
  c(14,14,0,14,0,2),#6
  c(6,6,6,6,6,6),#7
  c(0,6,18,0,0,6),#14
  c(0,0,12,12,12,12),#21
  c(0,0,0,0,0,12),#42
  c(2,2,2,2,2,1),#rk
  c(0,0,0,0,0,1)#Ab
)
M78=cbind(
  c(13,1,3,13,39,1),#2
  c(26,26,2,2,2,2),#3
  c(26,26,0,26,0,2),#6
  c(12,12,12,12,12,12),#13
  c(0,12,36,0,0,12),#26
  c(0,0,24,24,24,24),#39
  c(0,0,0,0,0,24),#78
  c(2,2,2,2,2,1),#rk
  c(0,0,0,0,0,1)#Ab
)
M110=cbind(
  c(11,1,5,11,55,1),#2
  c(44,44,4,4,4,4),#5
  c(44,44,0,44,0,4),#10
  c(10,10,10,10,10,10),#11
  c(0,10,50,0,0,10),#22
  c(0,0,40,40,40,40),#55
  c(0,0,0,0,0,40),#110
  c(2,2,2,2,2,1),#rk
  c(0,0,0,0,0,1)#Ab
)
M114=cbind(
  c(19,1,3,19,57,1),#2
  c(38,38,2,2,2,2),#3
  c(38,38,0,38,0,2),#6
  c(18,18,18,18,18,18),#19
  c(0,18,54,0,0,18),#38
  c(0,0,36,36,36,36),#57
  c(0,0,0,0,0,36),#114
  c(2,2,2,2,2,1),#rk
  c(0,0,0,0,0,1)#Ab
)
#7: 375,605,903,1705
#8: 510,690,870,910,1122,1190,1330,1395,1410,1590,1610,1770,1914,2002
#9: 308,532,644,836,868,1316,1364,1652,1748,1815,1876,1892
#10: 90,132,198,276,306,350,414,490,522,564,650,708,738,846,850,852,950,954,996,1062,1078,1150,1274,1278,1284,1450,1485,1494,1572,1602,1666,1690,1694,1818,1850,1862,1926,2004,2034
M90=cbind(#10
  c(9,5,45,1,5,3,15,9,45,1),#2
  c(2,2,2,2,8,8,8,8,8,8),#3
  c(4,4,4,4,4,4,4,4,4,4),#5
  c(0,10,0,2,40,6,30,0,0,8),#6
  c(6,6,6,6,0,0,0,0,0,0),#9
  c(36,0,0,4,0,12,0,36,0,4),#10
  c(8,8,8,8,32,32,32,32,32,32),#15
  c(0,30,0,6,0,0,0,0,0,0),#18
  c(0,0,0,8,0,24,0,0,0,32),#30
  c(24,24,24,24,0,0,0,0,0,0),#45
  c(0,0,0,24,0,0,0,0,0,0),#90
  c(2,2,2,1,2,2,2,3,3,2),#rk
  c(0,0,0,1,0,0,0,0,0,1)#Ab
)
#11: 140  364  380  460  476  572  748  819  860  940  988 1036 1148 1180 1196 1276 1292 1340 1484 1564 1580 1612 1628 1660 1708 1804 1953 2044
#12: 88  152  184  196  204  210  248  330  344  348  376  390  462  472  484  492  536  568  570  632  636  664  714  770  824  856  858  966 1016 1048 1068 1110 1112 1208 1212 1230 1254 1290 1304 1326 1336 1356 1430 1432 1444 1518 1528 1592 1644 1688 1722 1784 1788 1794 1816 1870 1912 1938 1974 2008 2010 2030 2046
M88=cbind(#12
  c(1,1,1,23,45,3,25,3,5,1,47,7),#2
  c(2,2,46,24,2,44,22,4,2,6,0,0),#4
  c(44,4,0,0,0,0,0,0,0,0,0,0),#8
  c(10,10,10,10,10,10,10,10,10,10,10,10),#11
  c(10,10,10,10,10,30,30,30,50,10,30,70),#22
  c(20,20,20,20,20,0,0,40,20,60,0,0),#44
  c(0,40,0,0,0,0,0,0,0,0,0,0),#88
  c(2,1,2,2,2,2,2,2,2,2,3,3),#rk
  c(0,1,0,0,0,0,0,1,0,0,0,1)#Ab
)

#sub!!
#13: 56   60  150  189  441  726  837  945 1012 1161 1204 1521 1575 1647 1734 1809 1988
M56=cbind(#13
  c(1,1,1,15,29,3,17,3,5,1,7,31,7),#2
  c(2,2,30,16,2,28,14,4,2,6,0,0,0),#4
  c(6,6,6,6,6,6,6,6,6,6,48,6,6),#7
  c(28,4,0,0,0,0,0,0,0,0,0,0,0),#8
  c(6,6,6,6,6,18,18,18,30,6,0,18,42),#14
  c(12,12,12,12,12,0,0,24,12,36,0,0,0),#28
  c(0,24,0,0,0,0,0,0,0,0,0,0,0),#56
  c(8,8,12,16,16,16,16,16,16,12,6,32,32),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,3,3),#rk
  c(0,1,0,0,0,0,0,1,0,0,0,0,1)#Ab
)
M60=cbind(#13
  c(1,1,1,1,15,5,5,23,3,11,7,31,3),#2
  c(2,2,2,2,20,2,2,2,8,2,2,2,2),#3
  c(6,10,30,2,0,10,30,0,0,0,0,0,0),#4
  c(4,4,4,4,24,4,4,4,4,4,4,4,4),#5
  c(2,2,2,2,0,10,10,10,0,22,2,2,6),#6
  c(4,4,4,4,0,0,0,12,12,4,28,4,12),#10
  c(0,20,0,4,0,20,0,0,0,0,0,0,0),#12
  c(8,8,8,8,0,8,8,8,32,8,8,8,8),#15
  c(24,0,0,8,0,0,0,0,0,0,0,0,0),#20
  c(8,8,8,8,0,0,0,0,0,8,8,8,24),#30
  c(0,0,0,16,0,0,0,0,0,0,0,0,0),#60
  c(12,12,12,12,9,12,12,20,10,20,20,20,20),#sub
  c(2,2,2,1,2,2,2,2,2,2,2,2,2),#rk
  c(0,0,0,1,0,0,0,0,0,0,0,0,1)#Ab
)
#14: 16   36   40  104  232  296  351  424  488  808  872 1125 1192 1197 1256 1384 1448 1576 1755 1832
M16=cbind(#14
  c(1,3,7,3,3,3,9,5,1,7,11,3,7,15),#2
  c(2,12,8,12,4,4,2,6,10,8,4,12,8,0),#4
  c(4,0,0,0,8,8,4,4,4,0,0,0,0,0),#8
  c(8,0,0,0,0,0,0,0,0,0,0,0,0,0),#16
  c(5,15,17,13,11,10,11,10,9,27,27,19,20,67),#sub
  c(1,2,2,2,2,2,2,2,2,3,3,3,3,4),#rk
  c(1,1,0,0,1,0,0,0,0,1,0,0,0,1)#Ab
)
M36=cbind(#14
  c(1,1,3,19,3,1,1,1,9,15,3,7,19,3),#2
  c(2,2,2,2,2,8,8,8,8,8,26,8,8,8),#3
  c(18,2,0,0,0,6,18,2,18,0,0,0,0,0),#4
  c(2,2,6,2,6,8,8,8,0,12,6,20,8,24),#6
  c(6,6,24,6,6,0,0,0,0,0,0,0,0,0),#9
  c(0,4,0,0,0,12,0,16,0,0,0,0,0,0),#12
  c(6,6,0,6,18,0,0,0,0,0,0,0,0,0),#18
  c(0,12,0,0,0,0,0,0,0,0,0,0,0,0),#36
  c(9,9,8,15,15,14,18,18,10,22,14,22,30,30),#sub
  c(2,1,2,2,2,2,3,2,2,2,2,2,3,2),#rk
  c(0,1,0,0,1,0,0,1,0,0,0,0,0,1)#Ab
)
M40=cbind(#14
  c(1,1,1,1,11,21,3,13,3,5,1,11,23,7),#2
  c(2,2,10,22,12,2,20,10,4,2,6,20,0,0),#4
  c(4,4,4,4,4,4,4,4,4,4,4,4,4,4),#5
  c(20,4,20,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,4,4,4,4,12,12,12,20,4,4,12,28),#10
  c(8,8,0,8,8,8,0,0,16,8,24,0,0,0),#20
  c(0,16,0,0,0,0,0,0,0,0,0,0,0,0),#40
  c(8,8,8,12,16,16,16,16,16,16,12,16,32,32),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,3,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,1)#Ab
)
M104=cbind(#14
  c(1,1,1,1,27,53,3,29,3,5,1,27,55,7),#2
  c(2,2,26,54,28,2,52,26,4,2,6,52,0,0),#4
  c(52,4,52,0,0,0,0,0,0,0,0,0,0,0),#8
  c(12,12,12,12,12,12,12,12,12,12,12,12,12,12),#13
  c(12,12,12,12,12,12,36,36,36,60,12,12,36,84),#26
  c(24,24,0,24,24,24,0,0,48,24,72,0,0,0),#52
  c(0,48,0,0,0,0,0,0,0,0,0,0,0,0),#104
  c(8,8,8,12,16,16,16,16,16,16,12,16,32,32),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,3,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,1)#Ab
)
#15: 24,54,81,84,136,220,228,250,260  328  340  372  513  516  580  584  620  625  686  712  740  776  804  884  891  904  948  999 1060 1096 1236 1375 1377 1420 1460 1508 1524 1544 1668 1780 1812 1863 1864 1911 1924 1928 1940 1956 1971 1972
M24=cbind(#15 (2^3 3)
  c(1,1,1,1,7,13,3,9,3,5,1,9,7,15,7),#2
  c(2,2,8,2,2,2,2,2,2,2,2,8,8,2,2),#3
  c(2,2,6,14,8,2,12,6,4,2,6,6,0,0,0),#4
  c(2,2,8,2,2,2,6,6,6,10,2,0,8,6,14),#6
  c(12,4,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,0,4,4,4,0,0,8,4,12,0,0,0,0),#12
  c(0,8,0,0,0,0,0,0,0,0,0,0,0,0,0),#24
  c(8,8,7,12,16,16,16,16,16,16,12,11,12,32,32),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,2,3,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,0,1)#Ab
)
M54=cbind(#15 (2 3^3)
  c(27,1,9,3,9,9,27,9,1,1,1,3,9,27,1),#2
  c(2,2,8,8,26,8,8,26,8,26,8,26,26,26,26),#3
  c(0,2,18,6,18,18,0,18,8,26,8,24,18,0,26),#6
  c(6,6,18,18,0,18,18,0,18,0,18,0,0,0,0),#9
  c(0,6,0,18,0,0,0,0,18,0,18,0,0,0,0),#18
  c(18,18,0,0,0,0,0,0,0,0,0,0,0,0,0),#27
  c(0,18,0,0,0,0,0,0,0,0,0,0,0,0,0),#54
  c(8,8,14,14,16,13,20,22,20,22,16,32,32,56,56),#sub
  c(2,1,2,2,2,2,3,3,2,2,2,2,3,4,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,0,1)#Ab
)
M81=cbind(#15 (3^4)
  c(2,8,26,8,8,8,44,26,62,8,26,80,26,26,80),#3
  c(6,72,54,72,18,18,36,54,18,72,54,0,54,54,0),#9
  c(18,0,0,0,54,54,0,0,0,0,0,0,0,0,0),#27
  c(54,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#81
  c(5,23,23,17,14,12,20,14,16,13,50,56,38,33,212),#sub
  c(1,2,2,2,2,2,2,2,2,2,3,3,3,3,4),#rk
  c(1,1,0,0,1,0,0,0,0,0,1,0,0,0,1)#Ab
)
M84=cbind(#15 (2^2 3 7)
  c(1,1,1,1,1,1,15,31,3,3,3,15,7,43,3),#2
  c(14,14,2,2,2,2,14,2,14,8,56,2,2,2,2),#3
  c(14,2,6,14,42,2,0,0,0,0,0,0,0,0,0),#4
  c(14,14,2,2,2,2,42,14,42,0,0,30,2,2,6),#6
  c(6,6,6,6,6,6,6,6,6,6,6,6,6,6,6),#7
  c(28,28,0,28,0,4,0,0,0,0,0,0,0,0,0),#12
  c(6,6,6,6,6,6,6,18,18,18,18,6,42,6,18),#14
  c(0,0,12,12,12,12,0,12,0,48,0,12,12,12,12),#21
  c(0,12,36,0,0,12,0,0,0,0,0,0,0,0,0),#28
  c(0,0,12,12,12,12,0,0,0,0,0,12,12,12,36),#42
  c(0,0,0,0,0,24,0,0,0,0,0,0,0,0,0),#84
  c(12,12,12,12,12,12,20,20,20,10,10,20,20,20,20),#sub
  c(2,2,2,2,2,1,2,2,2,2,2,2,2,2,2),#rk
  c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,1)#Ab
)
#16: 100,126,234,405,550,558,676,774,812,1098,1156,1206,1218,1422,1550,1746,1854
M100=cbind(#16 (2^2 5^2)
  c(1,1,25,51,3,1,1,1,5,5,25,25,35,11,51,3),#2
  c(50,2,50,0,0,10,50,2,10,50,50,50,0,0,0,0),#4
  c(4,4,4,4,4,24,24,24,24,24,24,24,24,24,24,24),#5
  c(4,4,0,4,12,24,24,24,20,20,0,0,40,64,24,72),#10
  c(0,8,0,0,0,40,0,48,40,0,0,0,0,0,0,0),#20
  c(20,20,20,20,20,0,0,0,0,0,0,0,0,0,0,0),#25
  c(20,20,0,20,60,0,0,0,0,0,0,0,0,0,0,0),#50
  c(0,40,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#100
  c(9,9,9,15,15,16,24,24,13,13,24,16,24,24,40,40),#sub
  c(2,1,2,2,2,2,3,2,2,2,3,2,2,2,3,2),#rk
  c(0,1,0,0,1,0,0,1,0,0,0,0,0,0,0,1)#Ab
)
M126=cbind(#16 (2 3^2 7)
  c(7,1,9,7,63,1,7,3,21,1,7,3,21,9,63,1),#2
  c(2,2,2,2,2,2,44,44,44,44,8,8,8,8,8,8),#3
  c(14,2,0,14,0,2,56,42,42,44,56,6,42,0,0,8),#6
  c(6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6),#7
  c(42,42,6,6,6,6,0,0,0,0,0,0,0,0,0,0),#9
  c(0,6,54,0,0,6,0,18,0,6,0,18,0,54,0,6),#14
  c(42,42,0,42,0,6,0,0,0,0,0,0,0,0,0,0),#18
  c(12,12,12,12,12,12,12,12,12,12,48,48,48,48,48,48),#21
  c(0,12,0,0,0,12,0,0,0,12,0,36,0,0,0,48),#42
  c(0,0,36,36,36,36,0,0,0,0,0,0,0,0,0,0),#63
  c(0,0,0,0,0,36,0,0,0,0,0,0,0,0,0,0),#126
  c(12,12,12,12,12,12,24,18,18,24,24,18,18,24,24,24),#sub
  c(2,2,2,2,2,1,2,2,2,2,2,2,2,3,3,2),#rk
  c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,1)#Ab
)
#17: 675
#18: 156  342  444  666  732  876  930 1164 1308 1314 1830 1884 1962
#19: 1029
#20: 820 1220 1530 2020
#21: 1875
#23: 294 1014
#24: 546  798 1302 1482 1554
#27: 1210
#29: 1380
#30: 270  396  594  828  918  990 1242 1566 1692 1750 1806
#32: 630 1170 1386
#34: 450  924  980 1672 1932
#35: 616 1064 1288 1736 1820
#36: 612  700 1044 1476 1540 1710 1900 1908
#37: 180 1020 1740
#38: 1372 1650
#39: 264  552  750  760  920 1128 1144 1416 1704 1720 1880 1976 1992
#40: 280  660  728 1050 1428 1452 1716 1950

M32=cbind(#51 2^5
  c(1,7,3,3,7,11,11,3,11,3,7,3,3,3,3,3,3,17,9,1,7,15,7,7,11,3,19,15,7,11,11,3,7,19,3,7,7,7,19,11,3,11,15,7,15,23,7,15,19,11,31),#2
  c(2,24,12,12,8,20,4,12,12,20,16,12,20,20,4,4,4,2,10,18,24,16,24,24,20,28,12,16,24,20,20,28,24,12,28,8,8,8,4,12,20,12,8,16,16,8,24,16,12,20,0),#4
  c(4,0,16,16,16,0,16,16,8,8,8,16,8,8,24,8,8,4,4,4,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,16,16,16,8,8,8,8,8,8,0,0,0,0,0,0,0),#8
  c(8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,16,16,8,8,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#16
  c(16,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#32
  c(6,38,22,20,25,26,23,19,25,21,22,19,18,18,15,14,13,14,13,12,54,66,46,38,47,35,65,47,37,39,38,28,30,54,34,38,34,31,38,34,30,31,34,30,118,118,78,82,83,73,374),#sub
  c(1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,4,4,4,4,4,4,5),#rk
  c(1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,1,0,0,0,0,0,1)#Ab
)
M48=cbind(#52 AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA
  c(1,1,3,7,7,13,25,1,3,3,3,3,3,15,17,5,13,1,7,3,7,3,3,3,9,5,1,1,13,7,7,3,7,3,15,27,15,23,11,7,19,7,19,7,11,3,7,19,15,15,31,15),#2
  c(2,2,32,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,8,8,8,8,8,8,2,2,2,2,2,2,2,2,2,2,2,2,2,2,8,8,32,2,2),#3
  c(2,2,12,8,8,14,2,26,4,4,28,28,28,16,2,14,6,18,24,12,8,12,4,4,2,6,10,18,6,24,8,12,8,28,16,4,16,8,20,24,12,24,12,8,4,12,8,12,0,0,0,0),#4
  c(2,2,0,2,2,2,2,2,6,6,6,6,6,6,10,10,2,2,14,6,14,6,6,6,18,10,2,8,8,8,8,24,8,6,6,6,6,10,10,2,2,14,14,14,22,6,14,8,24,0,14,30),#6
  c(4,4,0,16,16,4,4,4,24,24,0,0,0,0,12,12,12,12,0,0,0,0,8,8,4,4,4,12,12,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,0,4,4,4,4,4,8,8,8,8,8,8,4,4,12,12,0,24,16,24,8,8,4,12,20,0,0,0,16,0,16,8,8,8,8,4,4,12,12,0,0,16,8,24,16,0,0,0,0,0),#12
  c(24,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#16
  c(8,8,0,8,8,8,8,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,16,16,8,8,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#24
  c(0,16,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#48
  c(10,10,10,22,20,20,22,18,22,20,30,26,26,34,22,20,20,18,34,30,34,26,22,20,22,20,18,13,16,19,19,18,15,38,54,54,40,54,40,38,40,54,54,54,54,38,40,33,39,34,134,134),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,2,2,3,4,4),#rk
  c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1)#Ab
)
M72=cbind(#50 (2^3 3^2)
  c(1,1,1,1,19,37,3,21,3,5,1,1,1,1,21,7,39,7,1,7,19,13,25,1,1,1,7,13,3,9,1,19,37,3,21,3,5,1,9,21,9,9,21,15,19,31,7,15,39,7),#2
  c(2,2,2,2,2,2,2,2,2,2,2,8,8,8,2,2,2,2,8,8,8,8,8,8,26,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,26,26,26,8,8,26,8,8,8),#3
  c(2,2,6,38,20,2,36,18,4,2,6,2,2,2,18,0,0,0,18,24,12,18,6,30,6,14,8,2,12,6,38,20,2,36,18,4,2,6,18,18,54,6,18,0,36,0,0,0,0,0),#4
  c(2,2,2,2,2,2,6,6,6,10,2,8,8,8,6,14,6,14,8,20,8,32,20,8,26,8,20,32,24,36,8,8,8,24,24,24,40,8,0,24,0,18,6,30,8,32,38,48,24,56),#6
  c(36,4,0,0,0,0,0,0,0,0,0,12,36,4,0,0,0,0,36,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,36,0,0,0,0,0,0,0,0,0,0,0),#8
  c(6,6,24,6,6,6,6,6,6,6,6,0,0,0,24,24,6,6,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#9
  c(4,4,12,4,4,4,0,0,8,4,12,16,16,16,0,0,0,0,0,12,24,0,12,24,12,40,28,16,24,12,16,16,16,0,0,32,16,48,0,0,0,12,0,0,0,0,0,0,0,0),#12
  c(6,6,24,6,6,6,18,18,18,30,6,0,0,0,0,24,18,42,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#18
  c(0,8,0,0,0,0,0,0,0,0,0,24,0,32,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#24
  c(12,12,0,12,12,12,0,0,24,12,36,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#36
  c(0,24,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#72
  c(12,12,11,18,24,24,24,24,24,24,18,19,24,24,18,20,48,48,14,35,37,35,37,27,20,27,35,35,37,37,36,48,48,48,48,48,48,36,10,26,14,24,30,26,26,69,32,69,96,96),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,3,2,2,2,3,3,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,2,2,2,2,2,2,2,3,2,2,3,2,3,3,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,1)#Ab
)
M80=cbind(#52 (2^4 5)
  c(1,1,1,11,11,21,41,1,3,3,3,3,3,23,25,5,21,1,7,3,7,3,3,3,9,5,1,11,11,11,11,3,3,23,3,23,43,23,35,15,11,31,7,27,7,11,3,7,15,23,47,15),#2
  c(2,2,2,12,12,22,2,42,4,4,44,44,44,24,2,22,6,26,40,12,8,12,4,4,2,6,10,12,12,52,52,20,20,40,44,24,4,24,12,32,36,16,40,20,8,4,12,8,0,40,0,0),#4
  c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,64,4,4,4),#5
  c(4,4,20,24,24,4,4,4,40,40,0,0,0,0,20,20,20,20,0,0,0,0,8,8,4,4,4,40,40,0,0,40,40,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,4,4,4,4,4,4,12,12,12,12,12,12,20,20,4,4,28,12,28,12,12,12,36,20,4,4,4,4,4,12,12,12,12,12,12,12,20,20,4,4,28,28,28,44,12,28,0,12,28,60),#10
  c(40,8,40,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#16
  c(8,8,8,8,8,8,8,8,16,16,16,16,16,16,8,8,24,24,0,48,32,48,16,16,8,24,40,8,8,8,8,0,0,0,16,16,16,16,8,8,24,24,0,0,32,16,48,32,0,0,0,0),#20
  c(16,16,0,16,16,16,16,16,0,0,0,0,0,0,0,0,0,0,0,0,0,0,32,32,16,16,16,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#40
  c(0,32,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#80
  c(10,10,10,22,20,20,22,18,22,20,30,26,26,34,22,20,20,18,34,30,34,26,22,20,22,20,18,22,20,30,26,22,20,34,38,54,54,40,54,40,38,40,54,54,54,54,38,40,17,54,134,134),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,2,3,4,4),#rk
  c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,1)#Ab
)
M108=cbind(#45 (2^2 3^3)
  c(1,1,3,55,3,1,1,1,1,1,1,1,1,1,9,39,27,3,3,3,3,3,19,7,19,19,55,19,3,3,3,1,1,1,1,9,9,15,39,27,3,7,19,55,3),#2
  c(2,2,2,2,2,8,8,26,8,8,26,8,26,8,26,8,26,26,26,8,8,80,8,8,26,8,8,26,8,26,8,26,26,26,26,26,26,26,26,26,80,26,26,26,26),#3
  c(54,2,0,0,0,18,6,18,18,54,18,2,2,2,18,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,6,18,54,2,18,54,0,0,0,0,0,0,0,0),#4
  c(2,2,6,2,6,8,8,26,8,8,26,8,26,8,18,24,54,6,6,24,24,24,44,20,62,44,8,62,24,78,24,26,26,26,26,18,18,66,42,54,24,74,62,26,78),#6
  c(6,6,6,6,6,18,18,0,18,18,0,18,0,18,0,18,0,54,54,72,72,0,18,18,0,18,18,0,18,0,18,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#9
  c(0,4,0,0,0,36,12,36,36,0,36,16,52,16,36,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,48,36,0,52,36,0,0,0,0,0,0,0,0,0),#12
  c(6,6,18,6,18,18,18,0,18,18,0,18,0,18,0,18,0,18,18,0,0,0,18,54,0,18,18,0,54,0,54,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#18
  c(18,18,72,18,18,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#27
  c(0,12,0,0,0,0,36,0,0,0,0,36,0,36,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#36
  c(18,18,0,18,54,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#54
  c(0,36,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#108
  c(12,12,11,20,20,22,22,25,20,30,33,30,33,24,17,34,39,23,19,26,22,28,34,34,39,32,50,55,50,55,40,52,52,84,84,24,24,54,76,54,62,76,76,140,140),#sub
  c(2,1,2,2,2,2,2,2,2,3,3,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,2,2,2,2,3,4,3,2,2,2,3,2,3,2,3,4,3),#rk
  c(0,1,0,0,1,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,1)#Ab
)
M112=cbind(#43 (2^4 7)
  c(1,1,15,15,29,57,1,3,3,3,3,3,31,33,5,29,1,7,3,7,3,3,3,9,5,1,3,31,59,31,47,19,15,43,7,35,7,11,3,7,15,63,15),#2
  c(2,2,16,16,30,2,58,4,4,60,60,60,32,2,30,6,34,56,12,8,12,4,4,2,6,10,60,32,4,32,16,44,48,20,56,28,8,4,12,8,0,0,0),#4
  c(6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,48,6,6),#7
  c(4,4,32,32,4,4,4,56,56,0,0,0,0,28,28,28,28,0,0,0,0,8,8,4,4,4,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(6,6,6,6,6,6,6,18,18,18,18,18,18,30,30,6,6,42,18,42,18,18,18,54,30,6,18,18,18,18,30,30,6,6,42,42,42,66,18,42,48,42,90),#14
  c(56,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#16
  c(12,12,12,12,12,12,12,24,24,24,24,24,24,12,12,36,36,0,72,48,72,24,24,12,36,60,24,24,24,24,12,12,36,36,0,0,48,24,72,48,0,0,0),#28
  c(24,24,24,24,24,24,24,0,0,0,0,0,0,0,0,0,0,0,0,0,0,48,48,24,24,24,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#56
  c(0,48,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#112
  c(10,10,22,20,20,22,18,22,20,30,26,26,34,22,20,20,18,34,30,34,26,22,20,22,20,18,38,54,54,40,54,40,38,40,54,54,54,54,38,40,17,134,134),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,2,4,4),#rk
  c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,1)#Ab
)
M120=cbind(#47 (2^3 3 5)
  c(1,1,1,1,1,1,1,11,7,31,17,41,37,1,1,1,11,21,3,13,1,7,13,3,9,1,31,61,3,33,3,5,1,25,31,23,9,33,23,11,11,47,7,23,15,63,7),#2
  c(2,2,2,2,20,2,2,2,2,2,2,2,2,2,8,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,20,20,2,8,8,8,2,2,2,8,2,2,2,2),#3
  c(2,2,2,2,30,10,10,36,40,16,30,6,10,46,6,22,12,2,20,10,14,8,2,12,6,62,32,2,60,30,4,2,6,30,0,40,6,30,0,20,60,0,0,0,0,0,0),#4
  c(4,4,4,4,24,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,24,24,4,4,4,4,4,4,4,4,4,4,4,4),#5
  c(2,2,2,2,20,2,2,22,2,2,22,22,2,2,8,2,22,42,6,26,2,2,2,6,6,2,2,2,6,6,6,10,2,20,20,10,0,0,40,22,22,22,8,46,6,6,14),#6
  c(12,20,60,4,0,20,60,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,4,4,24,4,4,4,28,4,28,4,28,4,4,4,4,4,12,12,4,28,52,12,36,4,4,4,12,12,12,20,4,0,24,12,36,12,12,4,4,28,28,12,60,12,28),#10
  c(4,4,4,4,0,20,20,0,20,20,0,0,20,20,0,44,24,4,40,20,4,4,4,0,0,4,4,4,0,0,8,4,12,0,0,20,0,0,0,40,0,0,0,0,0,0,0),#12
  c(8,8,8,8,0,8,8,8,8,8,8,8,8,8,32,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,0,0,8,32,32,32,8,8,8,32,8,8,8,8),#15
  c(8,8,8,8,0,0,0,24,0,24,0,24,0,24,24,8,8,8,0,0,56,32,8,48,24,8,8,8,0,0,16,8,24,0,0,0,24,0,0,0,0,0,0,0,0,0,0),#20
  c(0,40,0,8,0,40,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#24
  c(8,8,8,8,0,8,8,8,8,8,8,8,8,8,32,8,8,8,24,24,8,8,8,24,24,8,8,8,24,24,24,40,8,0,0,0,0,0,0,8,8,8,32,24,24,24,56),#30
  c(48,0,0,16,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#40
  c(16,16,16,16,0,0,0,0,0,0,0,0,0,0,0,16,16,16,0,0,16,16,16,0,0,16,16,16,0,0,32,16,48,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#60
  c(0,0,0,32,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#120
  c(16,16,16,16,12,16,16,32,32,32,32,32,32,24,14,24,32,32,32,32,24,32,32,32,32,24,32,32,32,32,32,32,24,19,22,32,22,22,24,32,32,64,24,64,64,64,64),#sub
  c(2,2,2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,2,3,3,3,3),#rk
  c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)#Ab
)
M168=cbind(#57
  c(1,1,1,1,1,1,1,15,29,3,17,15,7,43,21,57,49,1,3,5,1,1,1,1,15,29,3,17,1,7,13,3,9,1,43,85,3,45,3,5,1,21,7,7,9,45,31,31,31,63,7,7,7,31,15,87,7),#2
  c(14,14,2,2,2,2,14,14,14,14,14,2,2,2,2,2,2,2,14,14,14,8,56,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,56,56,2,8,8,14,8,56,2,14,8,56,2,2,2,2),#3
  c(2,2,2,2,2,2,30,16,2,28,14,48,56,20,42,6,14,62,4,2,6,6,6,30,16,2,28,14,14,8,2,12,6,86,44,2,84,42,4,2,6,42,0,0,6,42,0,0,0,0,0,0,0,0,0,0,0),#4
  c(14,14,2,2,2,2,14,42,70,42,70,30,2,2,30,30,2,2,42,70,14,8,56,2,30,58,6,34,2,2,2,6,6,2,2,2,6,6,6,10,2,0,56,14,0,0,98,56,56,30,98,8,56,62,6,6,14),#6
  c(6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,48,48,48,6,6,6,6,6,6,6,6,6,6,6,6,6),#7
  c(28,4,12,28,84,4,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(28,28,4,4,4,4,84,56,28,56,28,0,28,28,0,0,28,28,56,28,84,0,0,60,32,4,56,28,4,4,4,0,0,4,4,4,0,0,8,4,12,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#12
  c(6,6,6,6,6,6,6,6,6,18,18,6,42,6,42,6,42,6,18,30,6,6,6,6,6,6,18,18,6,42,78,18,54,6,6,6,18,18,18,30,6,0,0,0,54,18,18,18,18,42,42,42,42,18,90,18,42),#14
  c(0,0,12,12,12,12,0,0,0,0,0,12,12,12,12,12,12,12,0,0,0,48,0,12,12,12,12,12,12,12,12,12,12,12,12,12,12,12,12,12,12,0,0,96,48,48,0,48,0,12,0,48,0,12,12,12,12),#21
  c(56,56,0,56,0,8,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#24
  c(12,12,12,12,12,12,12,12,12,0,0,36,0,36,0,36,0,36,24,12,36,36,36,12,12,12,0,0,84,48,12,72,36,12,12,12,0,0,24,12,36,0,0,0,36,0,0,0,0,0,0,0,0,0,0,0,0),#28
  c(0,0,12,12,12,12,0,0,0,0,0,12,12,12,12,12,12,12,0,0,0,48,0,12,12,12,36,36,12,12,12,36,36,12,12,12,36,36,36,60,12,0,0,0,0,0,0,0,0,12,0,48,0,36,36,36,84),#42
  c(0,24,72,0,0,24,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#56
  c(0,0,24,24,24,24,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,24,24,24,0,0,24,24,24,0,0,24,24,24,0,0,48,24,72,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#84
  c(0,0,0,0,0,48,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#168
  c(16,16,16,16,16,16,24,32,32,32,32,32,32,32,32,32,32,24,32,32,24,14,14,24,32,32,32,32,24,32,32,32,32,24,32,32,32,32,32,32,24,15,12,12,22,22,64,24,24,64,64,24,24,64,64,64,64),#sub
  c(2,2,2,2,2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,2,2,3,3,2,2,3,3,3,3),#rk
  c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1),#Ab
  c(46,40,20,28,44,16,78,110,142,98,130,128,112,160,144,192,176,96,80,100,60,30,84,60,92,124,68,100,36,52,68,44,60,108,172,236,116,180,32,40,24,179,104,50,60,180,226,148,178,336,160,52,112,196,108,372,64)#ss
)
M200=cbind(#52
  c(1,1,1,1,51,101,3,53,3,5,1,51,103,7,1,1,1,1,1,1,1,11,51,21,61,1,1,11,21,3,13,1,51,101,3,53,3,5,1,25,35,35,45,25,11,11,51,51,71,23,103,7),#2
  c(2,2,50,102,52,2,100,50,4,2,6,100,0,0,2,2,2,10,10,50,50,60,20,50,10,70,22,12,2,20,10,102,52,2,100,50,4,2,6,50,60,100,50,150,20,100,100,100,0,0,0,0),#4
  c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24,24),#5
  c(100,4,100,0,0,0,0,0,0,0,0,0,0,0,20,100,4,20,100,100,100,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,100,0,0,0,0,0,0,0,0,0,0,0,0),#8
  c(4,4,4,4,4,4,12,12,12,20,4,4,12,28,24,24,24,24,24,24,24,64,24,104,64,24,24,64,104,72,112,24,24,24,72,72,72,120,24,0,40,40,80,0,64,64,24,24,104,152,72,168),#10
  c(8,8,0,8,8,8,0,0,16,8,24,0,0,0,48,48,48,40,40,0,0,40,80,0,40,80,128,88,48,80,40,48,48,48,0,0,96,48,144,0,40,0,0,0,80,0,0,0,0,0,0,0),#20
  c(20,20,20,20,20,20,20,20,20,20,20,20,20,20,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#25
  c(0,16,0,0,0,0,0,0,0,0,0,0,0,0,80,0,96,80,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#40
  c(20,20,20,20,20,20,60,60,60,100,20,20,60,140,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#50
  c(40,40,0,40,40,40,0,0,80,40,120,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#100
  c(0,80,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),#200
  c(12,12,12,18,24,24,24,24,24,24,18,24,48,48,22,32,32,18,18,32,22,38,42,38,42,30,30,38,38,42,42,48,64,64,64,64,64,64,48,17,34,38,29,21,34,34,64,42,74,74,128,128),#sub
  c(2,1,2,2,2,2,2,2,2,2,2,2,3,3,2,3,2,2,2,3,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,2,2,2,2,2,2,2,2,2,2,3,2,3,3,3,3),#rk
  c(0,1,0,0,0,0,0,0,1,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)#Ab
)
}
if(l==64){load(system.file("M64.RData",package="grouptheory"))}
if(l==96){load(system.file("M96.RData",package="grouptheory"))}
if(l==128){load(system.file("M128.RData",package="grouptheory"))}#ok
if(l==144){load(system.file("M144.RData",package="grouptheory"))}
if(l==160){load(system.file("M160.RData",package="grouptheory"))}
if(l==192){load(system.file("M192.RData",package="grouptheory"))}
if(l==240){load(system.file("M240.RData",package="grouptheory"))}
if(l==288){load(system.file("M288.RData",package="grouptheory"))}
if(l==320){load(system.file("M320.RData",package="grouptheory"))}#ok
if(l==360){load(system.file("M360.RData",package="grouptheory"))}
if(l==384){load(system.file("M384.RData",package="grouptheory"))}
if(l==400){load(system.file("M400.RData",package="grouptheory"))}
if(l==480){load(system.file("M480.RData",package="grouptheory"))}
if(l==576){load(system.file("M576.RData",package="grouptheory"))}
if(l==600){load(system.file("M600.RData",package="grouptheory"))}
if(l==640){load(system.file("M640.RData",package="grouptheory"))}#ok
if(l==720){load(system.file("M720.RData",package="grouptheory"))}
if(l==960){load(system.file("M960.RData",package="grouptheory"))}#ok
if(l==1200){load(system.file("M1200.RData",package="grouptheory"))}
if(l==1440){load(system.file("M1440.RData",package="grouptheory"))}
    #############################
    Aw=Relabel(A,w)
    ab=IsAbelian(Aw)
    ord=c(OrderStructure(Aw),rk,ab)
    
    M=get(paste0("M",l)); nM=ncol(M); nd=length(Divisors(l))
    if(nM==nd+2){
      oo=FindRows(ord,M)
    }
    if(nM==nd+3){
      oo=FindRows(ord,M[,c(1:nd,nd+2,nd+3)])
      if(length(oo)>1){
        nsu=NumberOfSubgroups(Aw)
        oo=intersect(oo,which(M[,nd+1]==nsu[1]))
      }
    }
    if(nM==nd+4){
      oo=FindRows(ord,M[,c(1:nd,nd+2,nd+3)])
      if(length(oo)>1){
        nsu=NumberOfSubgroups(Aw)
        oo=intersect(oo,which(M[,nd+1]==nsu[1]))
        oo=intersect(oo,which(M[,nd+4]==nsu[2]))
      }
    }
    if(length(oo)>1){out=-100}#paste(oo,collapse=".")}
    else{out=oo}
  }
  return(out)
}
```

# YfromMAX

```{r function-YfromMAX}
#' YfromMAX
#'
#' @param M,A,X The matrix group "M", its Cayley table "A", and its list of up-to-conjugacy-subgroups "X".
#'
#' @return A list of identifiers of the groups
#' 
#' @export
#'
#' @examples
YfromMAX=function(M,A,X){
  dd=c(); n=nrow(M[[1]]); mid=-1
  for(j in 1:length(M)){
    if(det(M[[j]])<0){dd=c(dd,j)}
    if(sum((M[[j]]+diag(rep(1,n)))^2)<0.01){mid=j}
  }
  ox=c()
  for(j in 1:length(X)){#print(j)
    w=X[[j]]; x=w[3]; ww=w[-c(1,2,3)]; o1=o2=0
    if(length(intersect(ww,dd))>0){o1=1}
    if(length(intersect(ww,mid))>0){o2=1}
    type=GroupId(A,ww,x)
    ox=rbind(ox,c(w[1],type,w[2],x,o1,o2))
  }
  return(ox)
}
```

# NamesfromY

```{r function-NamesfromY}
#' YNamesfromY
#'
#' @param Y The matrix group "M", its Cayley table "A", and its list of up-to-conjugacy-subgroups "X".
#'
#' @return The names of the groups
#' 
#' @export
#'
#' @examples
NamesfromY=function(Y){
  out=c()
  for(j in 1:nrow(Y)){
    size=Y[j,1]; type=Y[j,2]
    if(type==0 | type== -100){out=c(out,paste0(size,".?","(",j,")"))}
    if(type>0){out=c(out,paste0(size,".",type,"(",j,")"))}
    if(size==21 & type==-4){out=c(out,paste0("21.1","(",j,")"))}
    if(type==-3){out=c(out,paste0("D",size,"(",j,")"))}
    if(size==4 & type==-2){out=c(out,paste0("K",4,"(",j,")"))}
    if(size==9 & type==-2){out=c(out,paste0("Z3^2","(",j,")"))}
    if(type==-1){out=c(out,paste0("Z",size,"(",j,")"))}
    
  }
  return(out)
}
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_first.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
